DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
reviewed experimental evaluation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Regarding the state-space representation, we can check the physical plant expressed by 
Eq.~\eqref{ss-synth-controller} (describing a pendulum control system), that the feedback matrix 
(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the physical plant 
with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

@@

\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

@@

The synthesized controllers are validated to be stable using the MATLAB step reponse, 
which means that our results are reliable for control engineers. A link to the full experimental environment, 
including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website.\footnote{\url{www.dsverifier.org}}

>>>>

Regarding the state-space representation, we have reproduced the stability property for 
the closed-loop control system of a pendulum represented by Eq.~\eqref{ss-synth-controller}. 
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

@@

For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
by the \tool is also stable, as shown in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

@@

The digital controllers synthesized by \tool are all stable using the MATLAB step response
as a validation procedure, which means that our results are reliable for control engineers. 
A link to the full experimental environment, including the scripts to reproduce the results, 
all benchmarks, videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
